Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-19 SDSS-2023/testing-charts-accuracy.qmd
a few wording changes on first figure

Participants were recruited as part of NORC's AmeriSpeak panel, which utilizes a probability-based sampling methodology and samples U.S. households from NORC's National Sample Frame that provides coverage of over 97% of U.S. households.
The current panel size is 54,001 panel members aged 13 and over residing in over 43,000 households **CITE DENNIS 2022** @dennis2019technical. \hh{I don't think I've got the right citation}
Each test was conducted using the AmeriSpeak Omnibus survey, which runs biweekly and samples around 1,000 U.S. adults to answer questions on a variety of topics.

@@

The data used for assessing the accuracy of comparisons in \autoref{tbl-tasks-12} is collected in two rounds of the NORC Omnibus survey.
Rounds 1 and 2 are combined by adjusting the weights with $\lambda$ = `r round(lambda[1],3)` for an effective sample size of `r round(neff(round_12$weight),1)`.
Figure \ref{fig-alignment}(a) shows that more than twice the number of responses is accurate, when the tiles are aligned along the same axis.
Because each participant was shown both versions of the chart, we can use a paired $t$-test to compare mean accuracy between the two charts.
The resulting $t$-statistic is highly significant ($t$ statistic: `r round(paired$statistic,1)`, df: `r paired$parameter`, $p$-value: \< 2.2e-16).

```{r accuracy,   warning=FALSE}
#| fig-cap: "On the left (a), a stacked barchart shows the number of respondents with correct (green) and incorrect (grey) responses to the two comparison questions. When tiles are aligned along the same axis, more than twice the number of responses is accurate. The shaded area along the top of the green tiles corresponds to  95\\% confidence intervals around (marginal) correct responses. On the right (b), a parallel coordinate plot shows all combinations of responses. There's a huge asymmetry in the number of responses where participants answered only one of the questions correctly. A lot more responses are correct when comparing aligned tiles than unaligned tiles."
#| label: fig-alignment
#| out-width: 80%
#| fig-height: 5 
#| fig-width: 10

>>>>

Participants were recruited as part of NORC's AmeriSpeak panel, which utilizes a probability-based sampling methodology and samples U.S. households from NORC's National Sample Frame that provides coverage of over 97% of U.S. households.
The current panel size is 54,001 panel members aged 13 and over residing in over 43,000 households **CITE DENNIS 2022**.
Each test was conducted using the AmeriSpeak Omnibus survey, which runs biweekly and samples around 1,000 U.S. adults to answer questions on a variety of topics.

@@

The data used for assessing the accuracy of comparisons in \autoref{tbl-tasks-12} is collected in two rounds of the NORC Omnibus survey.
Rounds 1 and 2 are combined by adjusting the weights with $\lambda$ = `r round(lambda[1],3)` for an effective sample size of `r round(neff(round_12$weight),1)`.
Figure \ref{fig-alignment}(a) shows that more than twice the number of responses are correct, when the tiles are aligned along the same axis.
Because each participant was shown both versions of the chart, we can use a paired $t$-test to compare mean accuracy between the two charts. 
The resulting $t$-statistic is highly significant ($t$ statistic: `r round(paired$statistic,1)`, df: `r paired$parameter`, $p$-value: \< 2.2e-16).

```{r accuracy,   warning=FALSE}
#| fig-cap: "On the left (a), a stacked barchart shows the number of respondents with correct (green) and incorrect (grey) responses to the two comparison questions. When tiles are aligned along the same axis, more than twice the number of responses are correct. The shaded area along the top of the green tiles corresponds to  95\\% confidence intervals around (marginal) correct responses. On the right (b), a parallel coordinate plot shows all combinations of responses. There's a huge asymmetry in the number of responses where participants answered only one of the questions correctly. A lot more responses are correct when comparing aligned tiles than unaligned tiles."
#| label: fig-alignment
#| out-width: 80%
#| fig-height: 5 
#| fig-width: 10
